Supplementary information for Marine species do not need visas: the transboundary nature of the world’s exploited marine species

### 2020-08-12 Scripts/supplements.Rmd

```{r Call_Sup_1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch. The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon."}

@@

```{r Call_Sup_4, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis"}

@@

>>>>

```{r Call_Sup_1, eval = T, fig.width = 12, fig.height = 10, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch. The number of species is displayed in the EEZ while catch (in thousand tonnes) is displayed in the land polygon. Figure created using R version 3.5.2. Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively."}

@@

```{r Call_Sup_4, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis. Figure created using R version 3.5.2."}

@@

We report the average fishing revenue of 2005 to 2014 derived from the fishing activity within the global EEZs.
